\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE A
%====================
\vspace*{6pt}
\subsection{{Research Intern }\hfill May 2022 - August 2022}
\subtext{ONES Technology \hfill Ankara/Turkey}
\begin{zitemize}
\item Obtained broad technical and R\&D knowledge, with practical experience in electrical component storage and soldering, complementing my engineering expertise.
\item Studying STM32 microcontroller circuit design and libraries enhanced my understanding of fundamental microcontroller circuit design and programming.
\end{zitemize}

%==================== 
% EXPERIENCE B 
%==================== 
\vspace*{6pt}
\subsection{{Engineering Intern }\hfill April 2022 - May 2022}
\subtext{SAIMOS by ONG-IT GmbH \hfill Vienna/Austria}
\begin{zitemize}
\item Developed expertise in HTTP Request methods using Postman and Curl apps, and reinforced my understanding by mastering the Kotlin language and its Ktor add-on.
\item Learned how to use Git for collaborative teamwork on projects.
\end{zitemize}

%==================== 
% EXPERIENCE C 
%==================== 
\vspace*{6pt}
\subsection{{Engineering Intern }\hfill  July 2021 - August 2021}
\subtext{Pimser Security Solutions \hfill Ankara/Turkey}
\begin{zitemize}
\item Researched CCTV and Access Control Systems, Computer Information, and their practical applications.
\item Had a beginner tutorial on how to use AutoCAD and use project management knowledge to design a beginner project with other co-workers.
\end{zitemize}
%==================== 
% EXPERIENCE D 
%==================== 
\vspace*{6pt}
\subsection{{Engineering Intern }\hfill May 2021 - July 2021}
\subtext{AGMLab \hfill Ankara/Turkey}
\begin{zitemize}
\item As an IT department employee at a company specializing in automation, cloud informatics, and optimization, I gained experience working with MATLAB, C++, and their add-ons.
\item Working on a new project and laying its foundations gave me insight into overall project management and working independently.
\end{zitemize}

\end{document}
